A Survey of Sterile Neutrinos

### 2015-04-14 p3_505/paper/paper3.tex

\section{Current and Future Experimental Efforts}
Due to the number of anomalous results to date sterile neutrino searches have become popular research topics at the majority of contemporary neutrino experiments, both those currently running and those in the design and construction phases.
\subsection{Current}
% Matt
\subsubsection{MINOS/MINOS+}
The MINOS (Main Injector Neutrino Oscillation Search) experiment ran from 2005 to 2012 and its upgraded second run, MINOS+, has taking data since September 2013. The MINOS experiment is a long baseline style detector with a neutrino beam source and near detector at Fermilab and a far detector located in northern Minnesota. Though it's primary physics goals lie in the area of neutrino oscillation measurements, MINOS and MINOS+ are now also running sterile neutrino analysis with their data. MINOS detects sterile nutrinos via their disappearence in neutral-current (NC) and

The latest results \cite{MINOS+} are still in preprint but

@@

\subsection{Future}
% Matt
NOVA
MicroBooNE
DUNE (Formerly LBNE)

>>>>

\section{Current and Future Experimental Efforts}
Due to the number of anomalous results to date sterile neutrino searches have become popular research topics at the majority of contemporary neutrino experiments, both those currently running and those in the design and construction phases.
\subsection{Current Experiments}
%Matt
\subsubsection{MINOS/MINOS+}
The MINOS (Main Injector Neutrino Oscillation Search) experiment ran from 2005 to 2012 and its upgraded second run, MINOS+, has taking data since September 2013. The MINOS experiment is a long baseline style detector with a neutrino beam source and near detector at Fermilab and a far detector located in northern Minnesota. Though it's primary physics goals lie in the area of neutrino oscillation measurements, MINOS and MINOS+ are now also running sterile neutrino analysis with their data. MINOS detects sterile neutrinos via their disappearance in neutral-current (NC) interactions, which are independent of the three known neutrino flavors and their oscillations, and charged-current (CC) interactions differing from those predicted from the mixing of the three neutrinos of the standard model.

The latest sterile neutrino results from MINOS \cite{MINOS} are still in preprint but

@@

\subsection{Future Experiments}
%Matt
NOVA
MicroBooNE
DUNE (Formerly LBNE)
